---
title: "Progress Memo 1"
format: html
editor: visual
author: Sydney Newton
date: "October 29, 2023"
---

::: {.callout-tip icon="false"}
## Github Repo Link

[My GitHub Link](https://github.com/sydneynewton1/Newton_Sydney_progress_memo_1.git)
:::

## Libraries

```{r}
library(tidyverse)
library(naniar)
```

## Loading Data

```{r}
nfloffenses <- read_csv("data/nflOffensive2016.csv")
```

## Data source

I am using a dataset that shows the the offensive stats for every team in the NFL in 2016. I found this dataset on data.world It came as a csv and then I uploaded it to R using the function 'read_csv()'. The dataset contains 32 observations for each team and I am planning to use them all.

## Why this data

I chose this data for a few reasons. First, I have been a Kansas City Chiefs Fan since I was little. Because of this, I am a huge fan of the NFL and I understand the sport. I wanted to pick a dataset based in the NFL since I knew I would understand the variables. I chose this NFL dataset specifically because I am more interested in a team's offense than defense and I am interested to learn more about the different stats within each team.

## Data quality & complexity check

```{r}
miss_var_summary(nfloffenses)
```

There is no missingness issues for any of the 52 variables in this dataset. This will be beneficial when analyzing the data since I will not have to remove any N/A values.

## Potential data issues

There are some potential issues with my dataset. I will need to remove some of the 52 columns, such as 'RZ Md', 'RZ Att', and 'RZ Pct'. These variables are not relevant to my analysis. I will also have to rename some of the columns with confusing titles, like 'TOP' and 'Pen'. After some columns are removed and renamed, I think the data will be much easier to work with and there will be less issues.
